### 2011-09-18 doc/theses/vitasek/chapter-4-2-experiments-results.tex
Thesis: in progress

\subsection{Grammar and model generation}
\label{section-grammar-model-timing}

@@

The experimental set will contain $50 * (11 + 11) = 1100$ configurations: 50 iterations for 11 test data sets plus 11 sized test data sets. There will be no CHs or IHs. We will be gathering the timing data for IG extraction and model generation in GnuPlot format.

@@

\subsubsection{GLPK interface timing}

@@

A related problem is how long it takes to create input for GLPK and then parse its results. We will use the same test data sets as in the previous case, but now we will gather times needed to communicate with GLPK.

@@

\subsection{GLPK: native vs. Cygwin}

@@

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \heu{Glpk} CH set to a time limit from 1 to 46 seconds with increments of 5, meaning 10 settings * 50 iterations = 500 configurations in total (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights). The data set used is \dataset{100-500} as the biggest one in sized test data.

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 1}
\label{listing-experiment-glpk-native-vs-cygwin-1}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 50$}
	\FOR{$time = 1 \to 46$ step $5$}
    \STATE $ES \gets ES \cup {CH = \heu{Glpk}(limit = time), IH = \emptyset}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

The other way to compare the performance of these two GLPK versions is to see how long it takes them to find the optimum for a set of data of increasing size. This experimental set will contain 550 configurations for each version. Every configuration will let \heu{Glpk} CH run for unlimited time, until it finds the optimum. This will be repeated in 50 iterations for each of the 11 files from the sized test data set (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-2}). There will again be no IH, the only data we will collect are the times of the CH run in each case.

@@

\subsection{\heu{Random} vs. \heu{Fuzzy} vs. \heu{FIDAX}}

@@

We will be gathering the running time of the CH itself and quality of the best solution found for GnuPlot.

\begin{algorithm}
\caption{\heu{Random} vs. \heu{Fuzzy} vs. \heu{FIDAX} set generation}
\label{listing-experiment-random-fuzzy-fidax}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 50$}
	\FOR{$file \in $ official test data}
    \STATE $ES \gets ES \cup \{file, CH = \heu{Random}(pool = 10), IH = \emptyset\} \cup \{file, CH = \heu{Fuzzy}(pool = 10), IH = \emptyset\} \cup \{file, CH = \heu{FIDAX}, IH = \emptyset\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

We need a pool size of one and only a single iteration - both \heu{FIDAX} and \heu{Hungry} are deterministic. We will try all official data sets, first with empty IH, second with \heu{Hungry} as IH. We will gather the qualities in each case and see whether there is any improvement.

@@

% TODO for some reason \texttt{\textbf{vertex5}} looks only like \texttt{vertex5}
\begin{table}
  \caption{ID sets in \heu{FIDAX} versus \heu{FIDAX} + \heu{Hungry}}
  \bigskip
  \label{table-experiments-fidax-and-hungry-idsets}
  \centering
  \begin{tabular}{l | l}
  \heu{FIDAX} & \heu{FIDAX} + \heu{Hungry} \\
  \hline
                    & \texttt{\textbf{vertex5}}  \\
                    & \texttt{\textbf{vertex26}} \\
  \texttt{vertex30} & \texttt{vertex30} \\
  \texttt{vertex31} & \texttt{vertex31} \\
  \texttt{vertex32} & \texttt{vertex32} \\
  \texttt{vertex34} & \texttt{vertex34} \\
  \texttt{vertex35} & \texttt{vertex35} \\
  \texttt{vertex36} & \texttt{vertex36} \\
  \texttt{vertex37} & \texttt{vertex37} \\
  \texttt{vertex39} & \texttt{vertex39} \\
                    & \texttt{\textbf{vertex60}} \\
                    & \texttt{\textbf{vertex69}} \\
                    & \texttt{\textbf{vertex70}} \\
  \texttt{vertex74} & \texttt{vertex74} \\
  \texttt{vertex75} & \texttt{vertex75} \\
  \texttt{vertex80} & \texttt{vertex80} \\
  \end{tabular}
\end{table}

\subsection{Best standalone CH}

@@

We will use all the official data sets, set the pool size to 10 where applicable, $\alpha$ and $\beta$ to 1. This experiment will consist of 50 iterations * 11 data sets * 6 CHs = 3300 experimental configurations. See the Listing \ref{listing-experiment-best-standalone-ch} for details. This time we are not interested in run times, only in qualities which we shall gather in a format for GnuPlot.

\begin{algorithm}
\caption{Best Standalone CH set generation}
\label{listing-experiment-best-standalone-ch}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in $ official test data}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Fuzzy}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Incremental}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Removal}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{FIDAX}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Best IH for Glpk}

@@

This experimental set will contain 6 data sets * 50 iterations * 4 IHs = 1200 experimental configurations. Note that we are using only the most challenging data sets, as the combination of \heu{Glpk} as CH and any other IH is already an overkill for easier data sets.

\begin{algorithm}
\caption{Best IH for \heu{Glpk} set generation}
\label{listing-experiment-best-ih-for-glpk}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in \{\dataset{80-30}, \dataset{90-405}, \dataset{100-500}, \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}\}$}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Crossover}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Hungry}\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Local Branching}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

Setup used will be almost identical to that from the previous experiment. Experimental set will consist of 6 data sets * 50 iterations * 2 CHs = 600 experimental configurations, see Listing \ref{listing-experiment-ch-for-mutation}. We shall collect the eventual quality after running both the CH and the IH in format suited for GnuPlot.

\begin{algorithm}
\caption{\heu{Random} as CH set generation}
\label{listing-experiment-ch-for-mutation}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in \{\dataset{80-30}, \dataset{90-405}, \dataset{100-500}, \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}\}$}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

This experimental set will contain 5 different $\alpha$ settings * 5 $\beta$ settings * 8 data sets = 200 experimental configurations. We are not using the artificial data sets, because the way they are generated (attribute values are random numbers) they cannot possibly create different optimal ID sets. The pseudocode capturing this is in Listing \ref{listing-experiment-various-betas}. We will use \heu{Glpk} constrained to 1 second (thus making it an instance of \heu{Truncated Branch \& Bound}) and no IHs. Pool size as well as iteration count will be 1. We are noting the actual ID set found by the run of the heuristic.

\begin{algorithm}
\caption{Various values of $\alpha$ and $\beta$ set generation}
\label{listing-experiment-various-betas}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$\alpha \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
  \FOR{$\beta \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
    \FOR{$file \in $ realistic of converted official test data}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1, alpha = \alpha, beta = \beta), IH = \emptyset\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\begin{table}
  \caption{Different ID sets found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1}
  \centering
  \begin{tabular}{c || c}
    ID set \textbf{1}: element@attribute & ID set \textbf{2}: element@attribute \\
    \hline
    \texttt{aff@fa} & \texttt{aff@fa} \\
    \texttt{com@ty} & \texttt{com@ty} \\
    \texttt{cre@da} & \texttt{cre@da} \\
    \texttt{cri@te} & \texttt{cri@te} \\
    \texttt{cve@st} & \texttt{cve@st} \\
    \texttt{\textbf{def@id}} & \texttt{\textbf{def@cl}} <- \\ % TODO again, my bold typewriter does not work
    \texttt{fil@co} & \texttt{fil@co} \\
    \texttt{mod@da} & \texttt{mod@da} \\
    \texttt{ova@xs} & \texttt{ova@xs} \\
    \texttt{pat@op} & \texttt{pat@op} \\
    \texttt{sof@op} & \texttt{sof@op} \\
    \texttt{sta@da} & \texttt{sta@da} \\
    \texttt{sub@or} & \texttt{sub@or} \\
    \texttt{sbt@te} & \texttt{sbt@te} \\
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Effect of $\alpha$, $\beta$ on ID set found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-effect}
  \centering
  \begin{tabular}{c | c  c  c  c  c}
    $\alpha$ \textbackslash $\beta$ & 0.1 & 0.25 & 0.5 & 0.75 & 1 \\
    \hline
    0.1  & 1 & 2 & 2 & 1 & 1 \\
    0.25 & 2 & 2 & 2 & 1 & 2 \\
    0.5  & 2 & 1 & 1 & 1 & 2 \\
    0.75 & 1 & 2 & 1 & 2 & 1 \\
    1    & 1 & 2 & 1 & 1 & 2 \\
  \end{tabular}
\end{table}

\begin{table}
  \caption{Effect of $\alpha-ratio$ on ID set found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-ratio-effect}
  \centering
  \begin{tabular}{c | c || c |  c}
    $\alpha-ratio$ & ID set & $\alpha-ratio$ & ID set \\
    \hline
    0,091	& 1 & 0,500	& 2 \\
    0,118	& 1 & 0,500	& 2 \\
    0,167	& 2 & 0,571	& 1 \\
    0,200	& 2 & 0,600	& 1 \\
    0,250	& 1 & 0,667	& 1 \\
    0,286	& 2 & 0,667	& 1 \\
    0,333	& 2 & 0,714	& 2 \\
    0,333	& 2 & 0,750	& 2 \\
    0,400	& 1 & 0,800	& 2 \\
    0,429	& 1 & 0,833	& 2 \\
    0,500	& 1 & 0,882	& 1 \\
    0,500	& 2 & 0,909	& 1 \\
    0,500	& 1 &       &   \\
  \end{tabular}
\end{table}

@@

\subsection{Ignoring text data}

@@

Our experimental set will contain 50 iterations * 2 = 100 experimental configurations as described in Listing \ref{listing-experiment-ignore-text-data}. We will be using \heu{Glpk} limited to 1 second with no additional IH and pool size set to 1. After the first 50 iterations we will turn on the option to ignore the simple text node data and run the same 50 iterations again. We will be collecting the grammar extraction (GE) and model creation (MC) times as in the experiment in Section \ref{section-grammar-model-timing}.

\begin{algorithm}
\caption{Ignoring text data set generation}
\label{listing-experiment-ignore-text-data}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\STATE \textbf{set} ``ignore text data"
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

Data gathered will be traces like the one in Appendix \ref{appendix-trace} - after each iteration, the time taken so far and the quality of incumbent solution is noted.

\begin{algorithm}
\caption{Chaining IHs set generation}
\label{listing-experiment-chaining-ihs}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\STATE $\heu{MUT} \gets \heu{Mutation}(ratio = 0.1, limit = 1)$
\STATE $\heu{CX} \gets \heu{Crossover}(ratio = 0.1, limit = 1)$
\STATE $\heu{LB} \gets \heu{LocalBranching}(ratio = 0.1, limit = 1)$
\STATE $\heu{RR} \gets \heu{RandomRemove}(ratio = 0.1)$
\STATE $\heu{H} \gets \heu{Hungry}$
\STATE $\heu{RW} \gets \heu{RemoveWorst}$
\STATE $IHs \gets \emptyset$

@@

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} results for Strategy 1}
  \label{image-experiment-chained-ihs-s1}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s1}
\end{figure}

@@

In this particular example there is only 1 run out of 10 that does not finish (find optimum) under the 10 second mark.

There are two more graphs like this in Figures \ref{image-experiment-chained-ihs-s2} and \ref{image-experiment-chained-ihs-s3} for comparison, capturing Strategy 2 and Strategy 3 respectively working on the same data set, \dataset{100-100}. Describing them in detail is unfortunately outside of the scope of this work.

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} results for Strategy 2}
  \label{image-experiment-chained-ihs-s2}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s2}
\end{figure}

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} results for Strategy 3}
  \label{image-experiment-chained-ihs-s3}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s3}
\end{figure}

It is now necessary to assess which of the strategies perform the best. We shall take a look at the different data sets. Easily we can discard \dataset{MSH}, \dataset{NTH}, \dataset{XMA-c}, \dataset{XMA-p}, because the optimum is found in the very first step. Let us now introduce a metric for assessment of a strategy: namely, how many times of the 20 runs did it find the optimum. Results of this are summarized in Table \ref{table-experiments-chained-ihs-tweaking}.

\begin{table}
  \caption{Performance of various IH chains}
  \bigskip
  \label{table-experiments-chained-ihs-tweaking}
  \centering
  \begin{tabular}{l || c | c | c}
    Dataset & Strategy 1 & Strategy 2 & Strategy 3 \\
    \hline
    \dataset{100-100}  & \textbf{20} & 19 & \textbf{20} \\
    \dataset{100-200}  & \textbf{19} & 18 & 17 \\
    \dataset{100-1000} & 4  & 1  & \textbf{5}  \\
    \dataset{OVA1}     & \textbf{20} & \textbf{20} & \textbf{20} \\
    \dataset{OVA2}     & \textbf{19} & 13 & 18 \\
    \dataset{OVA3}     & 17 & 18 & \textbf{20} \\
    \end{tabular}
  \bigskip
  Each cell represents the number of times (out of 20) the strategy found the optimum - more is better.
\end{table}

>>>>

\subsection{Grammar and Model Generation}
\label{section-grammar-model-timing}

@@

The experimental set will contain $50 * (11 + 11) = 1100$ configurations: 50 iterations for 11 test data sets plus 11 sized test data sets. There will be no CHs or IHs. We will be gathering the timing data for IG extraction and model generation in GnuPlot format.\\

@@

\subsubsection{GLPK Interface Timing}

@@

A related problem is how long it takes to create input for GLPK and then parse its results. We will use the same test data sets as in the previous case, but now we will gather times needed to communicate with GLPK.\\

@@

\subsection{GLPK: Native vs. Cygwin}

@@

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \heu{Glpk} CH set to a time limit from 1 to 46 seconds with increments of 5, meaning 10 settings * 50 iterations = 500 configurations in total (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights). The data set used is \dataset{100-500} as the biggest one in sized test data.\\

\begin{algorithm}
\caption{GLPK: Native vs. Cygwin Set Generation 1}
\label{listing-experiment-glpk-native-vs-cygwin-1}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 50$}
	\FOR{$time = 1 \to 46$ step $5$}
    \STATE $ES \gets ES \cup {CH = \heu{Glpk}(limit = time), IH = \emptyset}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

The other way to compare the performance of these two GLPK versions is to see how long it takes them to find the optimum for a set of data of increasing size. This experimental set will contain 550 configurations for each version. Every configuration will let \heu{Glpk} CH run for unlimited time, until it finds the optimum. This will be repeated in 50 iterations for each of the 11 files from the sized test data set (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-2}). There will again be no IH, the only data we will collect are the times of the CH run in each case.\\

@@

\subsection{\heu{Random} vs. \heu{Fuzzy} vs. \heu{FIDAX}}
\label{section-experiments-random-fuzzy-fidax}

@@

We will be gathering the running time of the CH itself and quality of the best solution found for GnuPlot.\\

\begin{algorithm}
\caption{\heu{Random} vs. \heu{Fuzzy} vs. \heu{FIDAX} Set Generation}
\label{listing-experiment-random-fuzzy-fidax}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 50$}
	\FOR{$file \in $ official test data}
    \STATE $ES \gets ES \cup \{file, CH = \heu{Random}(pool = 10), IH = \emptyset\} \cup \{file, CH = \heu{Fuzzy}(pool = 10), IH = \emptyset\} \cup \{file, CH = \heu{FIDAX}, IH = \emptyset\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

We need a pool size of one and only a single iteration - both \heu{FIDAX} and \heu{Hungry} are deterministic. We will try all official data sets, first with empty IH, second with \heu{Hungry} as IH. We will gather the qualities in each case and see whether there is any improvement.\\

@@

% TODO for some reason \texttt{\textbf{vertex5}} looks only like \texttt{vertex5}
\begin{table}
  \caption{ID Sets in \heu{FIDAX} Versus \heu{FIDAX} + \heu{Hungry}}
  \bigskip
  \label{table-experiments-fidax-and-hungry-idsets}
  \centering
  \begin{tabular}{l | l}
  \heu{FIDAX} & \heu{FIDAX} + \heu{Hungry} \\
  \hline
                    & \texttt{\textbf{vertex5}}  \\
                    & \texttt{\textbf{vertex26}} \\
  \texttt{vertex30} & \texttt{vertex30} \\
  \texttt{vertex31} & \texttt{vertex31} \\
  \texttt{vertex32} & \texttt{vertex32} \\
  \texttt{vertex34} & \texttt{vertex34} \\
  \texttt{vertex35} & \texttt{vertex35} \\
  \texttt{vertex36} & \texttt{vertex36} \\
  \texttt{vertex37} & \texttt{vertex37} \\
  \texttt{vertex39} & \texttt{vertex39} \\
                    & \texttt{\textbf{vertex60}} \\
                    & \texttt{\textbf{vertex69}} \\
                    & \texttt{\textbf{vertex70}} \\
  \texttt{vertex74} & \texttt{vertex74} \\
  \texttt{vertex75} & \texttt{vertex75} \\
  \texttt{vertex80} & \texttt{vertex80} \\
  \end{tabular}
\end{table}

\subsection{Best Standalone CH}

@@

We will use all the official data sets, set the pool size to 10 where applicable, $\alpha$ and $\beta$ to 1. This experiment will consist of 50 iterations * 11 data sets * 6 CHs = 3300 experimental configurations. See the Listing \ref{listing-experiment-best-standalone-ch} for details. This time we are not interested in run times, only in qualities which we shall gather in a format for GnuPlot.\\

\begin{algorithm}
\caption{Best Standalone CH Set Generation}
\label{listing-experiment-best-standalone-ch}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in $ official test data}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Fuzzy}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Incremental}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Removal}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{FIDAX}, IH = \emptyset\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\subsection{Best IH for \heu{Glpk}}

@@

This experimental set will contain 6 data sets * 50 iterations * 4 IHs = 1200 experimental configurations. Note that we are using only the most challenging data sets, as the combination of \heu{Glpk} as CH and any other IH is already an overkill for easier data sets.\\

\begin{algorithm}
\caption{Best IH for \heu{Glpk} Set Generation}
\label{listing-experiment-best-ih-for-glpk}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in \{\dataset{80-30}, \dataset{90-405}, \dataset{100-500}, \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}\}$}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Crossover}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Hungry}\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Local Branching}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

Setup used will be almost identical to that from the previous experiment. Experimental set will consist of 6 data sets * 50 iterations * 2 CHs = 600 experimental configurations, see Listing \ref{listing-experiment-ch-for-mutation}. We shall collect the eventual quality after running both the CH and the IH in format suited for GnuPlot.\\

\begin{algorithm}
\caption{\heu{Random} as CH Set Generation}
\label{listing-experiment-ch-for-mutation}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$file \in \{\dataset{80-30}, \dataset{90-405}, \dataset{100-500}, \dataset{100-100}, \dataset{100-200}, \dataset{100-1000}\}$}
	\FOR{$i = 1 \to 50$}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1), IH = \heu{Mutation}(ratio = 0.1, limit = 1)\}$
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

This experimental set will contain 5 different $\alpha$ settings * 5 $\beta$ settings * 8 data sets = 200 experimental configurations. We are not using the artificial data sets, because the way they are generated (attribute values are random numbers) they cannot possibly create different optimal ID sets. The pseudocode capturing this is in Listing \ref{listing-experiment-various-betas}. We will use \heu{Glpk} constrained to 1 second (thus making it an instance of \heu{Truncated Branch \& Bound}) and no IHs. Pool size as well as iteration count will be 1. We are noting the actual ID set found by the run of the heuristic.\\

\begin{algorithm}
\caption{Various Values of $\alpha$ and $\beta$ Set Generation}
\label{listing-experiment-various-betas}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$\alpha \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
  \FOR{$\beta \in \{0.1, 0.25, 0.5, 0.75, 1\}$}
    \FOR{$file \in $ realistic of converted official test data}
    	\STATE $ES \gets ES \cup \{file, CH = \heu{Glpk}(limit = 1, alpha = \alpha, beta = \beta), IH = \emptyset\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\begin{table}
  \caption{Different ID Sets Found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1}
  \centering
  \begin{tabular}{c || c}
    ID set \textbf{1}: element@attribute & ID set \textbf{2}: element@attribute \\
    \hline
    \texttt{aff@fa} & \texttt{aff@fa} \\
    \texttt{com@ty} & \texttt{com@ty} \\
    \texttt{cre@da} & \texttt{cre@da} \\
    \texttt{cri@te} & \texttt{cri@te} \\
    \texttt{cve@st} & \texttt{cve@st} \\
    \texttt{\textbf{def@id}} & \texttt{\textbf{def@cl}} <- \\ % TODO again, my bold typewriter does not work
    \texttt{fil@co} & \texttt{fil@co} \\
    \texttt{mod@da} & \texttt{mod@da} \\
    \texttt{ova@xs} & \texttt{ova@xs} \\
    \texttt{pat@op} & \texttt{pat@op} \\
    \texttt{sof@op} & \texttt{sof@op} \\
    \texttt{sta@da} & \texttt{sta@da} \\
    \texttt{sub@or} & \texttt{sub@or} \\
    \texttt{sbt@te} & \texttt{sbt@te} \\
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Effect of $\alpha$, $\beta$ on ID Set Found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-effect}
  \centering
  \begin{tabular}{c | c  c  c  c  c}
    $\alpha$ \textbackslash $\beta$ & 0.1 & 0.25 & 0.5 & 0.75 & 1 \\
    \hline
    0.1  & 1 & 2 & 2 & 1 & 1 \\
    0.25 & 2 & 2 & 2 & 1 & 2 \\
    0.5  & 2 & 1 & 1 & 1 & 2 \\
    0.75 & 1 & 2 & 1 & 2 & 1 \\
    1    & 1 & 2 & 1 & 1 & 2 \\
  \end{tabular}
\end{table}

\begin{table}
  \caption{Effect of $\alpha-ratio$ on ID Set Found for \dataset{OVA1}}
  \bigskip
  \label{table-experiments-various-betas-ova1-ratio-effect}
  \centering
  \begin{tabular}{c | c || c |  c}
    $\alpha-ratio$ & ID set & $\alpha-ratio$ & ID set \\
    \hline
    0,091	& 1 & 0,500	& 2 \\
    0,118	& 1 & 0,500	& 2 \\
    0,167	& 2 & 0,571	& 1 \\
    0,200	& 2 & 0,600	& 1 \\
    0,250	& 1 & 0,667	& 1 \\
    0,286	& 2 & 0,667	& 1 \\
    0,333	& 2 & 0,714	& 2 \\
    0,333	& 2 & 0,750	& 2 \\
    0,400	& 1 & 0,800	& 2 \\
    0,429	& 1 & 0,833	& 2 \\
    0,500	& 1 & 0,882	& 1 \\
    0,500	& 2 & 0,909	& 1 \\
    0,500	& 1 &       &   \\
  \end{tabular}
\end{table}

@@

\subsection{Ignoring Text Data}

@@

Our experimental set will contain 50 iterations * 2 = 100 experimental configurations as described in Listing \ref{listing-experiment-ignore-text-data}. We will be using \heu{Glpk} limited to 1 second with no additional IH and pool size set to 1. After the first 50 iterations we will turn on the option to ignore the simple text node data and run the same 50 iterations again. We will be collecting the grammar extraction (GE) and model creation (MC) times as in the experiment in Section \ref{section-grammar-model-timing}.\\

\begin{algorithm}
\caption{Ignoring Text Data Set Generation}
\label{listing-experiment-ignore-text-data}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\STATE \textbf{set} ``ignore text data"
\FOR{$i \in 1 \to 50 $}
  \STATE $ES \gets ES \cup \{\dataset{XMA-p}, CH = \heu{Glpk}(limit = 1), IH = \emptyset\}$
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

Data gathered will be traces like the one in Appendix \ref{appendix-trace} - after each iteration, the time taken so far and the quality of incumbent solution is noted.\\

\begin{algorithm}
\caption{Chaining IHs Set Generation}
\label{listing-experiment-chaining-ihs}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\STATE $\heu{MUT} \gets \heu{Mutation}(ratio = 0.1, limit = 1)$
\STATE $\heu{CX} \gets \heu{Crossover}(ratio = 0.1, limit = 1)$
\STATE $\heu{LB} \gets \heu{LocalBranching}(ratio = 0.1, limit = 1)$
\STATE $\heu{RR} \gets \heu{RandomRemove}(ratio = 0.1)$
\STATE $\heu{H} \gets \heu{Hungry}$
\STATE $\heu{RW} \gets \heu{RemoveWorst}$
\STATE $IHs \gets \emptyset$

@@

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} Results for Scenario 1}
  \label{image-experiment-chained-ihs-s1}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s1}
\end{figure}

@@

In this particular example there is only 1 run out of 10 that does not finish (find optimum) under the 10 second mark.\\

There are two more graphs like this in Figures \ref{image-experiment-chained-ihs-s2} and \ref{image-experiment-chained-ihs-s3} for comparison, capturing Scenario 2 and Scenario 3 respectively working on the same data set, \dataset{100-100}. Describing them in detail is unfortunately outside of the scope of this work.\\

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} Results for Scenario 2}
  \label{image-experiment-chained-ihs-s2}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s2}
\end{figure}

\begin{figure}
  \caption{Chained IHs - \dataset{100-100} Results for Scenario 3}
  \label{image-experiment-chained-ihs-s3}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/chained-ihs-s3}
\end{figure}

It is now necessary to assess which of the scenarios perform the best. We shall take a look at the different data sets. Easily we can discard \dataset{MSH}, \dataset{NTH}, \dataset{XMA-c}, \dataset{XMA-p}, because the optimum is found in the very first step. Let us now introduce a metric for assessment of a scenario: namely, how many times of the 20 runs did it find the optimum. Results of this are summarized in Table \ref{table-experiments-chained-ihs-tweaking}.

\begin{table}
  \caption{Performance of Various IH Chains}
  \bigskip
  \label{table-experiments-chained-ihs-tweaking}
  \centering
  \begin{tabular}{l || c | c | c}
    Dataset & Scenario 1 & Scenario 2 & Scenario 3 \\
    \hline
    \dataset{100-100}  & \textbf{20} & 19 & \textbf{20} \\
    \dataset{100-200}  & \textbf{19} & 18 & 17 \\
    \dataset{100-1000} & 4  & 1  & \textbf{5}  \\
    \dataset{OVA1}     & \textbf{20} & \textbf{20} & \textbf{20} \\
    \dataset{OVA2}     & \textbf{19} & 13 & 18 \\
    \dataset{OVA3}     & 17 & 18 & \textbf{20} \\
    \end{tabular}
\end{table}

Each cell contains the number of times the scenario found optimum in the data set, out of 20 runs. Highlited are the scenarios that performed best on that data set. We see that Scenario 1 and 3 are very similar in performance. We shall nonetheless choose Scenario \textbf{1} as the winner for its simplicity. Now we can tune its parameters.

\subsubsection{Improving Scenario 1}
